\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Fix spelling
Fix typo

  \item[-] \textbf{Liason Judgement:} One among \textit{pending}, \textit{rejected} and \textit{accepted}.

@@

A normal uploading flow goes as follows \footnote{This is a highly information description which will be fleshed out in future drafts.}.

>>>>

  \item[-] \textbf{Liaison Judgement:} One among \textit{pending}, \textit{rejected} and \textit{accepted}.

@@

A normal uploading flow goes as follows \footnote{This is a highly informal description which will be fleshed out in future drafts.}.
